TBD

### 2020-11-02 outputs/paper/paper.Rmd
MODEL UPDATE

```{r}
attach(clean_survey)
mod <- brm(binary ~ age + education_grouped + race_ethnicity + hispanic + household_income_grouped + state + extra_covid_worn_mask,
           data = clean_survey,
           family = bernoulli(),
           iter = 4000
           )

@@

```{r}
usa_00001$estimate <-
  mod %>%
  predict(newdata = usa_00001)
```

>>>>

```{r}
attach(clean_survey)
mod <- brm(binary ~ age + (1|education_grouped) + race_ethnicity + hispanic + household_income_grouped + state + extra_covid_worn_mask,
           data = clean_survey,
           family = bernoulli(),
           iter = 4000,
           control = list(adapt_delta = 0.98)
           )

@@

```{r}
posterior_prob <- posterior_linpred(mod, transform = TRUE, newdata = post_strat_cellcount, allow_new_levels = TRUE)
poststrat_prob <- posterior_prob %*% post_strat_cellcount$n / sum(poststrat$n)
model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
round(model_popn_pref, 3)
```
